### 2019-04-04 papers/journal/conclusion.tex
Updated Pairing encoding for the SMT

\noindent 
%
\todo{Copid just to create a template}
We have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
%
Our results contain many predictions which can in
principle be tested through cell-biological experiments. 
%
However, our current knowledge of the actual vesicle transport graph of a cell is very poor: it is likely that there are many vesicle transport routes that are still uncharacterized. Even in those instances where vesicles are known to exist, the precise molecular drivers of their creation and fusion are often unknown.
%
Therefore, a direct verification of our predictions based on graph connectedness alone is not likely. 
%
However, more indirect predictions based on how SNAREs are regulated can be
explored. 
%
In this context, the Sec/MUNC proteins or SNARE longin domains are interesting
targets of study~\cite{van2010one,rossi2004longins}.

\todo{Copid just to create a template}In the experiments, we have demonstrated the power of SMT solvers and the
value of careful encoding of the problems into SMT queries. 
%
We manage to scale the tool upto the size that makes tool biologically relevant. However, there are many further search problems or extensions that are of interest. 
%
For example, are there any k-connected graphs that can not be annotated into a VTS? 
%
This problem induces a quantifier alternation in an encoding. Therefore, a simple call to SAT solver will not work. 
%
We are planning to use QBF(quantified Boolean
formulas) solvers or develop iterative search algorithm for such queries.
%
One may be interested in counting the number of graphs that satisfy a given
property. 
%
Exact counting of the graphs using SAT solvers may prove to be very
difficult. 
%
We are also planning to employ some methods for approximate counting
of solutions.

We do not have a complete picture of the VTS graph, and so far, discoveries of new vesicles and molecular components are being made by groups interested in finding the path of a particular molecule, or they are chance discoveries. 
%
\todo{Copied till para end! Need revision}In this paper, we presented encodings of the synthesis problems
that may arise from VTSs.
%
%
We demonstrated that our tool based on the encodings
scale up to the relevant sizes of the VTSs for some synthesis queries.
%
Our tool timed out on larger examples.
%
We are working to improve the performance of our tool.
%
%
With this tool, we made an attempt to present multiple new testable predictions. 
%
We will take this tool to the biologists and develop wet experiments that may validate some synthesis results from the tool.
%
These predictions may very likely increase to hasten discoveries in this field alongside pushing forward the use of formal methods in the biological field.

>>>>

\noindent 
%
\todo{Just a template}
We have established a connection between vesicle transport graph connectedness and underlying rules of SNARE pairing and regulation. 
%
Our results contain many predictions which can in
principle be tested through cell-biological experiments. 
%
However, our current knowledge of the actual vesicle transport graph of a cell is very poor: it is likely that there are many vesicle transport routes that are still uncharacterized. Even in those instances where vesicles are known to exist, the precise molecular drivers of their creation and fusion are often unknown.
%
Therefore, a direct verification of our predictions based on graph connectedness alone is not likely. 
%
However, more indirect predictions based on how SNAREs are regulated can be
explored. 
%
In this context, the Sec/MUNC proteins or SNARE longin domains are interesting
targets of study~\cite{van2010one,rossi2004longins}.

%\todo{Copid just to create a template}
In the experiments, we have demonstrated the power of SMT solvers and the
value of careful encoding of the problems into SMT queries. 
%
We manage to scale the tool upto the size that makes tool biologically relevant. However, there are many further search problems or extensions that are of interest. 
%
For example, are there any k-connected graphs that can not be annotated into a VTS? 
%
This problem induces a quantifier alternation in an encoding. Therefore, a simple call to SAT solver will not work. 
%
We are planning to use QBF(quantified Boolean
formulas) solvers or develop iterative search algorithm for such queries.
%
One may be interested in counting the number of graphs that satisfy a given
property. 
%
Exact counting of the graphs using SAT solvers may prove to be very
difficult. 
%
We are also planning to employ some methods for approximate counting
of solutions.

We do not have a complete picture of the VTS graph, and so far, discoveries of new vesicles and molecular components are being made by groups interested in finding the path of a particular molecule, or they are chance discoveries. 
%
%\todo{Copied till para end! Need revision}
In this paper, we presented encodings of the synthesis problems
that may arise from VTSs.
%
%
We demonstrated that our tool based on the encodings
scale up to the relevant sizes of the VTSs for some synthesis queries.
%
Our tool timed out on larger examples.
%
We are working to improve the performance of our tool.
%
%
With this tool, we made an attempt to present multiple new testable predictions. 
%
We will take this tool to the biologists and develop wet experiments that may validate some synthesis results from the tool.
%
These predictions may very likely increase to hasten discoveries in this field alongside pushing forward the use of formal methods in the biological field.

### 2019-04-04 papers/journal/intro.tex
Updated Pairing encoding for the SMT

%\ankit{Need more clarity on the importance and relevance of the CONNECTIVITY and it's relevance.}
One such benchmark is provided by our result about connectivity of the VTS graph. Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected. For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph. Therefore the underlying undirected graph is 2-connected. 
From our result, for a given set of biomolecular interactions, for a cell that is in steady state, we expect the VTS graph to have a certain k-connectivity. When regulation is given by arbitrary Boolean rules,   we find that VTS graphs must be 3-connected. And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected [28].

>>>>

%\ankit{Need more clarity on the importance and relevance of the CONNECTIVITY and it's relevance.}
One such benchmark is provided by our result about connectivity of the VTS graph. Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected. For example, in a directed cyclic graph, every node has at least one incoming and one outgoing edge, at least 2 edges need to be removed in order to disconnect the graph. Therefore the underlying undirected graph is 2-connected. 
From our result, for a given set of biomolecular interactions, for a cell that is in steady state, we expect the VTS graph to have a certain k-connectivity. When regulation is given by arbitrary Boolean rules, we find that VTS graphs must be 3-connected. And when we add the constraint of the specific form of regulatory interactions seen between VTS molecules, we expect vesicle transport graphs to be 2-strongly connected.
